\Huge{Machine Learning} \\ \LARGE Nature's Quest: Deep Learning Exploration of Global Plant Traits from Images and Geodata

### 2024-03-29 paper/paper.tex
add abstract

\begin{abstract}
    % Abstract content goes here
\end{abstract}

@@

\smallskip 
Upon visual inspection one of the first issues we spotted was a considerable chunk (29.53\%) of data missing for the auxiliary task standard deviations. Through some previous work on the same Kaggle, we noticed that the auxiliary data was a useful inclusion. We can also validate these reports with previous work applying auxiliary tasks in CNNs such as the work of Lukas Libel and Marco Kroener which found that the inclusion of an auxiliary task with minor relevance to the main task did indeed boost performance \cite{lukaslibel} and Chen et. al. \cite{pmlr-v80-chen18a} which demonstrated that for very similar or mostly similar auxiliary tasks the contribution is generally a positive one. Based on this we decided to use a simple k-nearest neighbor (kNN) imputation strategy which has generally proved effective \cite{joel2024performance}. The rest of the data had all values present.

>>>>

\begin{abstract}
    % Abstract content goes here
    Global warming and climate change have created concerns about the adaptation of plant species to constantly evolving environmental conditions. Monitoring and analyzing plant traits provides crucial insights into ecosystem responses to such changes. Convolutional Neural Networks (CNNs) offer a promising approach to predicting plant traits based on images, and related geological data. This paper explores the effectiveness of CNNs predicting relevant plant traits trained on images alone versus those trained on images combined with ancillary geodata. Our results indicate that while models trained on images and geodata converge faster, they do not necessarily outperform models trained on images alone. Further investigation into hyperparameters, model architectures, and data modifications is warranted to enhance the prediction capabilities of these models and understanding the relationship between plant traits and environmental factors.
\end{abstract}

@@

\smallskip 
Upon visual inspection one of the first issues we spotted was a considerable chunk (29.53\%) of data missing for the auxiliary task standard deviations. Through some previous work on the same Kaggle, we noticed that the auxiliary data was a useful inclusion. We can also validate these reports with previous work applying auxiliary tasks in CNNs such as the work of Lukas Libel and Marco Kroener which found that the inclusion of an auxiliary task with minor relevance to the main task did indeed boost performance \cite{lukaslibel} and Chen et. al. \cite{pmlr-v80-chen18a} which demonstrated that for very similar or mostly similar auxiliary tasks the contribution is generally a positive one. Based on this we decided to use a simple k-nearest neighbor (kNN) imputation strategy which has generally proven to be effective \cite{joel2024performance}. The rest of the data had all values present.
